---
title: "Wine Quality Cluster Analysis"
author: "neelani"
date: "June 25, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Background

Perform a clustering analysis to understand and classify the quality of the Wines.


## Data 

The data for this project is available here:
Data Source:  (http://archive.ics.uci.edu/ml/datasets/Wine+Quality)

### Available Attributes
- 1 - fixed acidity 
- 2 - volatile acidity 
- 3 - citric acid 
- 4 - residual sugar 
- 5 - chlorides 
- 6 - free sulfur dioxide 
- 7 - total sulfur dioxide 
- 8 - density 
- 9 - pH 
- 10 - sulphates 
- 11 - alcohol

## Model Design Approach

Create reactive R-Shiny web application to accept the input paratmeters listed as follows, perform the k-means clustering and prodce the scatter plot

- Number of Clusters
- Attributes Selection for Clustering 


### Read the data 

```{r data}
wine <- read.csv("WineStudy/winequality-red.csv", header=TRUE, sep=";")
```

### Initialize the variables - Simulate the web input

- Number of Clusters - 4
- Attributes Selected - Density and Alcohol

```{r init}

  no_cl <- 4
  x1 <- FALSE
  x2 <- FALSE
  x3 <- FALSE
  x4 <- FALSE
  x5 <- FALSE
  x6 <- FALSE
  x7 <- FALSE
  x8 <- TRUE
  x9 <- FALSE
  x10 <- FALSE
  x11 <- TRUE
  x12 <- FALSE

```  

### K-means clustering 

```{r cluster}  
  colsel <- c(x1, x2, x3, x4, x5, x6, x7, x8, x9, x10, x11, x12)
  
  wine_sel <- wine[, colsel]
  
  set.seed(1234)
  cl<-kmeans(wine_sel,  no_cl)
    
```

### Selected attributes summary

```{r sum, echo = TRUE}

summary(wine_sel)

```


### Plot the clusters

```{r plot, echo = TRUE}

# Plot Cluster Means 
plot(wine_sel, col=cl$cluster)

```
